Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-18 WRITEUP/ms.tex
done lens modeling sec

We first obtain a preliminary lens model for each channel slice independently,
where their lens parameters are allowed to vary and are initialized according
to the aforementioned way. We obtain the final model
by repeating the modeling over each slice but fixing their lens parameters
according to the overall median in the preliminary models
(see \Tab{lens}). This ensures the
lens model of each kinematic component share the same lens profile.
The magnification factor is determined by taking the ratio
between the image plane flux of the model and the source plane flux.
The source positions and magnification factors are listed in \Tab{model}.

% disk and caveat
The location of the reconstructed sources in \Fig{model} are consistent with
of a disk. This in essence demonstrate a velocity field in the source plane.
 While solely based on the lens model would not be sufficient to
draw such conclusion/assertion. Yet, with the observed velocity gradient.
We emphasis that the spatial resolution of is a few arcsec, which means that
although we have high SNR and spectral resolution, this data is not sufficient
to constrain the intrinsic sizes of the lensed galaxies, and thus underpredict
the magnification factors. We will discuss this further in the following
section.

% comparison with C06 model

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{
Lens models of RXJ1131 using \uvmcmcfit on the PdBI \bco data.
Lens model of channel widths $\sim$ 100\kms.
Make this bigger in the future
Top: Channel maps of the PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale). The location of the foreground lensing galaxy is indicated by a black dot and its critical curve is traced by the orange solid line. The locations and morphologies (half-light radii) of the reconstructed sources are
represented by magenta ellipses (see text in \Sec{lensmodel} for caveat). The caustic curves are shown as cyan lines.
The beam of the observations is shown in
the bottom right corner of each panel.
Bottom: Residual images of the best-fit model, obtained by
taking the Fourier transform after subtracting the best-fit model from the
data in the visibility plane.
Contours start at $\pm$3$\sigma$ and increment at steps of
3$\times$2$^n\sigma$, where $n$ is a positive integer.
\label{fig:model}}
\end{figure*}

>>>>

We first obtain a preliminary lens model for each channel slice independently,
where their lens parameters are allowed to vary and are initialized according
to the aforementioned way. We obtain the final model
by repeating the modeling over each slice but fixing their lens parameters
according to the overall median in the preliminary models, as listed in \Tab{lens}. The corresponding masses within the Einstein radii is
$M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun.
This ensures that all models share the same lens profile.
The magnification factor is determined by taking the ratio
between the image plane flux of the model and the source plane flux.
The best-fit magnification factors are listed in \Tab{model}.
We compare our model parameters in \Tab{lens} describing
the mass distribution of the lensing galaxy
against that of the SIE model presented by C06. The position
%\footnote{We note that they report a positional offset
% relative to the light centroid in the HST image, which are at slightly
%different astrometry. Our comparison takes into
%account the astrometric correction applied.}
of lensing mass, Einstein Radius, PA and axial ratio
are all consistent within the uncertainties.
% PA = -73.6, ellipticity = 0.45,
% their theta\_R = 1.84" $\pm$ 0.01.

\subsection{Interpretation and Caveats}
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient in the source plane, which is
indicative of a disk geometry. While solely based on the
lens model is insufficient to draw conclusive inference on its
true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
can be found in the observed (image plane) velocity field and
the double-horned line profile in \Fig{CO21spec}. Furthermore,
the reconstructed source plane emission in optical-NIR
is also best-reproduced using a $n$\,=\,1 Sersic profile (C06).
Our interpretation therefore tends in favor of a disk morphology for RXJ1131.

% the companion
One interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
separated by $\sim$2.4\,kpc away from the AGN host galaxy.

We emphasis that the spatial resolution of the data at hand
is a few arcsec, which implies that despite the high SNR and spectral
resolution, this data is insufficient to constrain the
intrinsic sizes of the lensed galaxies, and thus the magnification
factors is likely under-predicted. We will discuss this further in the following section. % magnification factor is underpredicted, see Bussmann15

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{Each panel corresponds to a lens model of RXJ1131 performed over a
channel slice $\sim$100\,\kms of the \bco data. Top: Channel maps of the
PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale).
The location of the foreground lensing galaxy is indicated by a black dot and
its critical curve is traced by the orange solid line. The locations and
morphologies (half-light radii) of the reconstructed sources are
represented by magenta ellipses (see text in \Sec{lensmodel} for caveats).
The caustic curves are represented as cyan lines. The beam of the
PdBI observations is shown in the bottom right corner of each panel.
Bottom: Residual images of the best-fit models, obtained by
taking the Fourier transform after subtracting the best-fit model from the
data in the $uv$-domain. Contours start
at $\pm$3$\sigma$ and increment at steps of 3$\times$2$^n\sigma$,
where $n$ is a positive integer.
\label{fig:model}}
\end{figure*}
